Think deep for reef resilience

### 2025-08-10 paper/paper_draft.qmd
Updated ECS values for GCMs and sources
Found an error in the GFDL-CM4 ECS value, text will need updating accordingly

::: {#tbl-gcms}
| Global Climate Model source | ECS value (°C) | Interpreted relative severity | Results found in |
|-----------------------|-----------------------|------------------------|-----------------------|
| EC-Earth3-Veg | 4.31 | High | **insert repo citation** |
| ACCESS-CM2 | 4.72 | High | **insert repo citation** |
| ACCESS-ESM1-5 | 3.87 | Intermediate | Main text |
| GFDL-CM4 | 2.9 | Low | **insert repo citation** |
| NorESM2-MM | 2.5 | Low | **insert repo citation** |

: Information for each GCM used in this investigation including ECS value, interpreted
relative severity and where results are individual GCM results are found. GCMs in context
with assessed plausible ranges of ECS values are displayed in [@sfig-ecs]. ACCESS-ESM1-5 is
taken as an intermediate model based on the range of ECS values, thus results are displayed
in the main text. ECS value sources: .
:::

\[**BG: Need to add my ECS value sources to table caption. (And also cite GCM paper
sources).**\]

>>>>

::: {#tbl-gcms}
| Global Climate Model source | ECS value (K) | Interpreted relative severity | Results found in |
|-----------------------|-----------------------|------------------------|-----------------------|
| EC-Earth3-Veg | 4.30 | High | **insert repo citation** |
| ACCESS-CM2 | 4.66 | High | **insert repo citation** |
| GFDL-CM4 | 4.1 | High | **insert repo citation** |
| ACCESS-ESM1-5 | 3.87 | Intermediate | Main text |
| NorESM2-MM | 2.5 | Low | **insert repo citation** |

: Information for each GCM used in this investigation including Equilibrium Climate
Sensitivity (ECS) value, interpreted relative severity and where results are individual GCM
results are found. GCMs in context with assessed plausible ranges of ECS values are
displayed in [@sfig-ecs]. ACCESS-ESM1-5 has an ECS closest to the midpoint of the
very-likely ECS range and was taken as an intermediate model with results displayed in the
main text. ECS values obtained from: [@sentman2025; @grose2023; @seland2020; @ziehn2020;
@wyser2020].
:::
